Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
All persona inputs fixed. Now to import new data

# Need to check hold out level
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

@@

# Need to check hold out
selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

# Need to Fix
selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

@@

# Need to Fix
selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p2_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c("",
                     'White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

# Need to Fix
selectInput("p2_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))

@@

# Need to Fix
selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p3_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p3_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

selectInput("p3_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p3_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p3_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p3_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p3_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p3_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p3_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p3_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

@@

# Need to Fix
selectInput("p3_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p3_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p3_race",
         label = "Race(s):",
         choices = c("",
                     'White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

# Need to Fix
selectInput("p3_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))

>>>>

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

@@

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "Atleast once a day"))

selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p2_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

selectInput("p2_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))

@@

selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "Atleast once a day"))

selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p3_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p3_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p3_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p3_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

selectInput("p3_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p3_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p3_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p3_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p3_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p3_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p3_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p3_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p3_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

selectInput("p3_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

selectInput("p3_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))
